% arara: xelatex
% arara: biber
% arara: xelatex

\documentclass[]{friggeri-cv}

%------------
\usepackage{enumitem}
\renewenvironment{entrylist}{%
  \begin{itemize}[leftmargin=1in] %[leftmargin=*,align=left,itemindent=-\dimexpr\labelwidth+\labelindent+\labelsep\relax]
}{%
  \end{itemize}
}
\renewcommand{\bfseries}{\headingfont\color{headercolor}}
\renewcommand{\entry}[4]{%
  \item[#1]
    \textbf{#2}%
    \hfill%
    {\footnotesize\addfontfeature{Color=lightgray} #3}\\%
    #4\vspace{\parsep}%
  }
%-------

\begin{document}
\header{Mikiko}{Bazeley}
       {Operations Analyst | Data Visualization Specialist}
% In the aside, each new line forces a line break
\begin{aside}
\section{skills}
R-
gglot, dplyr, tidyr
Excel-
vlookups, pivot tables, formulas
SQL
HTML, CSS
Python
\section{programs}
Tableau
Salesforce
MySQL, OracleSQ, MSSQL
ArcGIS,QGIS
Excel
\section{concentration}
 quantitative analysis
 data management
 reporting
data wrangling
  \section{references available}
\href{https://www.linkedin.com/in/michaeloverell}{Michael Overell}
\href{https://www.linkedin.com/in/jennsteele}{Jenn Steele}
\href{https://www.linkedin.com/pub/alfred-louie/a5/a46/281}{Alfred Louie} 
 \section{connect}
\href{https://www.linkedin.com/in/mikikobazeley}{linkedin}
\href{http://mikikobazeley.github.io}{personal site}
\href{https://angel.co/mikiko-bazeley}{angel.co}
\href{https://github.com/MMBazel}{github}
  \section{education}
B.A. Economics
2013
UC San Diego
  \section{about}
  home:
    SF, CA 94133
    ~
    mobile: 
    \href{tel:14159489641}{415.948.9641}
    ~
    email:
    \href{mailto:mmbazel@gmail.com}{mmbazel@gmail.com}
\end{aside}

\section{objective}
Use data analysis and operations knowledge to catalyze revenue
growth and transform the consumer experience

\section{experience}

\begin{entrylist}
%-------
  \entry
    {07/14---curr.}
    {Operations Specialist}
    {Digimarc, San Mateo}
    {\textit{Summary}: Use data analysis tools and visualization in order to assist rights holders with protection and enforcement through operationalizing efficiency in value-added products and services.\\ 

\textbf {Product Analysis}: 
\begin{itemize}
\item Utilized open source tools such as R (with packages ggplot2, dplyr, knitr) in order to provide insight for management team and key clients into the efficacy of company product. 
\item Responsible for analysis projects from data warehouse querying (MySQL/MSSQL/SQL Server) to exploration to presentation. 
\end{itemize}

\textbf {Operations Support}:  
\begin{itemize}
\item Utilized Sharepoint to create and populate knowledge base for internal stakeholders with original training material for sales education. 
\item Maintain internal Sharepoint sites to empower management to store and create protocols and standards for operations and sales. 
\end{itemize}

\textbf {Data Visualization}: 
\begin{itemize}
\item Created and scripted ad-hoc customer and operations reports for use in marketing collateral and relationship management using R, excel, Gliffy. 
\item Designed, wireframed and created proof-of-concept visual reports. 
\end{itemize}



\textbf {Salesforce administration}: 
\begin{itemize}
\item Created on-boarding process and accompanying documentation to increase user adoption rates, inform the implementation road map, and increase sales reporting accuracy.
\item Integrated third party automation tools such as Pardot, InsideView, LinkedIn Navigator with sandbox Salesforce instance to automate sales cycle. 
\item Utilized Dataloader, excel, and R to migrate and clean data between Salesforce and Dynamic instances.
\end{itemize}
}
  

%-------

  \entry
    {07/14---curr.}
    {Sales Operations Lead}
    {RecruitLoop, San Francisco}
    {\textit{Summary}: Managed lead generation and infrastructure scaling for sales and growth team at early-stage recruiting startup.\\

\textbf {Salesforce Administration}: 
\begin{itemize}
\item Customized Salesforce to create objects, applications, reports and dashboards to enable the sales team to meet their quotas.
\end{itemize}

\textbf {Research Team Management}:
\begin{itemize}
\item Hired and trained team of 10 freelancers, as well as handled billing and performance tracking, in order to scale volume of lead generation from 200 (leads/rep/month) to 2000 (leads/rep/month).
\end{itemize}

\textbf {Sales Operations}: 
\begin{itemize}
\item Researched, identified and integrated products for outbound sales that decreased cost of lead acquisition by half while scaling volume (including conducting vendor negotiations and intiating beta trials)
\end{itemize}

\textbf {Email Marketing}: 
\begin{itemize}
\item A/B tested subject line, body text and send time to increase email engagement rates by 30 percent, enabling sales team to identify and connect with prospects, while scaling email volume).
\end{itemize}
}

%-------
   \entry
    {12/13---04/14}
    {Business Operations and Accounts Manager}
    {eSalon, San Francisco}
    {
\textit{Summary}: Assisted management with record keeping and hospitality.\\ 

\textbf {Account Management}: 
\begin{itemize}
\item Managed billing, business communications, and account creation for clients of team of 10 employees.
\end{itemize}

\textbf {Operations}: 
\begin{itemize}
\item Provided great customer service and cultivated client relationships by leading employee training and maintaining employee calendars.
\end{itemize}
%-------
}
\end{entrylist}	

\section{projects}
\begin{entrylist}
%-------
  \entry
    {1/15}
    {Consultant}
    {FirstJob}
    {\textit{Summary}: Laid foundation for an outbound sales process.\\ 

\textbf {Referral}:\\
\href{https://www.linkedin.com/in/brettbazzini}{Brett Bazzini: Head of Sales at FirstJob,Inc. during this time}\\
\textbf {Referral}:\\
\href{https://www.linkedin.com/in/braydanyoung}{Braydan Young: Vice President of Business Development at First Job,Inc. during this time}
}
  

%-------
	
\end{entrylist}	
\end{document}